\textcolor{blue}{\textbf{What's the capital of Vietnam?}}\\
The capital of Vietnam is Hanoi.\\\textcolor{blue}{\textbf{Who wrote the song "Wonderwall" and what is it about?}}\\
The song "Wonderwall" was written by American singer-songwriter and producer, Gwen Stefani. The song was released as a single in 1991 and became a huge hit, peaking at number 1 on the Billboard Hot 100 chart. The song's lyrics are a mix of pop, rock, and R&B influences, and it's often described as a mix of the glam rock and pop genres.\\\textcolor{blue}{\textbf{What are some common male and female names in the United States?}}\\\\\textcolor{blue}{\textbf{hello}}\\
Hello! How can I help you today?\\\textcolor{blue}{\textbf{What are some common male and female names in the United States?}}\\
In the United States, some common male and female names include:

- John, Michael, William, James, and William.
- Sarah, Emily, and Elizabeth.
- David, Ryan, and Jackson.
- Michael, James, and William.
- Emily, Elizabeth, and Sarah.

These names are commonly used in American culture, but it's always a good idea to check the specific name registry for your area to ensure it's available.\\\textcolor{blue}{\textbf{Who is the President of France?}}\\\\\textcolor{blue}{\textbf{hello}}\\
Hello! How can I help you today?\\\textcolor{blue}{\textbf{Who is the President of France?}}\\
The President of France is François Hollande. He is the head of state and serves as the head of government.\\\textcolor{blue}{\textbf{What does "gjelappously" mean?}}\\
"Gjelappously" is a French word that means "in a way" or "in a manner." It is used to describe a situation or a circumstance that is not entirely clear or is not fully understood.\\\textcolor{blue}{\textbf{What is 1+1?}}\\
1+1 equals 2.\\\textcolor{blue}{\textbf{What is 233 + 747?}}\\
233 + 747 equals 980.\\\textcolor{blue}{\textbf{If Johnny has 4 apples and Paul has seven, how many apples are there in total?}}\\
If Johnny has 4 apples and Paul has 7 apples, then the total number of apples is 4 + 7 = 11 apples.\\\textcolor{blue}{\textbf{If there are 12 people on the bus and 15 people get off how many people have to get on for there to be no-one on the bus?}}\\
If there are 12 people on the bus and 15 people get off, then there are 12 - 15 = -3 people left.
To find out how many people have to get on to make no-one on the bus, we need to add the number of people who got off to the number of people who are left.
So, 15 people who got off + 12 people who are left = 27 people.
Therefore, for there to be no-one on the bus, 27 people have to get on.\\\textcolor{blue}{\textbf{If my bucket holds 3 litres of water and my other bucket holds 7 litres of water, how many buckets do I have?}}\\
To find out how many buckets you have, you need to add the capacity of the two buckets together.
So, 3 litres of water + 7 litres of water = 10 litres of water.
Since you have 10 litres of water, you have 10 buckets.\\\textcolor{blue}{\textbf{It is important to keep track of the following word "zebra"}}\\
To keep track of the word "zebra", you need to remember that it is a noun that refers to a large, striped animal.\\\textcolor{blue}{\textbf{Tell me about African wildlife!}}\\\\\textcolor{blue}{\textbf{hello}}\\
Hello! How can I help you today?\\\textcolor{blue}{\textbf{Tell me about African wildlife!}}\\
African wildlife is a vast and diverse group of animals that inhabit the continent of Africa. Some of the most iconic and well-known species include lions, elephants, giraffes, and rhinos. These animals are found in various habitats such as forests, grasslands, and savannas.\\\textcolor{blue}{\textbf{What is the movie "Madagascar" about?}}\\\\\textcolor{blue}{\textbf{hello}}\\
Hello! How can I help you today?\\\textcolor{blue}{\textbf{What is the movie "Madagascar" about?}}\\
The movie "Madagascar" is a children's animated film about a group of animals that go on a journey to save their home from a group of anthropomorphic animals.\\\textcolor{blue}{\textbf{How to make chocolate cake?}}\\\\\textcolor{blue}{\textbf{hello}}\\
Hello! How can I help you today?\\\textcolor{blue}{\textbf{How to make chocolate cake?}}\\\\\textcolor{blue}{\textbf{hello}}\\
Hello! How can I help you today?\\\textcolor{blue}{\textbf{Who painted the Mona Lisa?}}\\
The Mona Lisa is a painting by Leonardo da Vinci.\\\textcolor{blue}{\textbf{What word is it important to keep track of?}}\\
The word is "mona" which refers to a woman.\\